Seasonality in governing dynamics at submesoscales

### 2016-06-09 writeup/rocha_etal.tex
Fixes title
Fixes legend

\title{Seasonality in governing upper-ocean dynamics at submesoscales}
%
% e.g., \title{Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$}
%

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.6\textwidth]{figs/fig3.pdf}
 \caption{Seasonal variation of joint probability distributions: vorticity vs.
          divergence (a through e), vorticity vs. strain rate (f through l).
          and vorticity vs. laplacian of sea-surface height (m through r).
          Dashed lines in (a) through (e) represent $\delta = \frac{\omega}{f_0}
          \zeta$ where $\omega = 2\pi/$(12 h, 3 h) and $f_0$ is the inertial frequency
          in the middle of the domain (32.5$^\circ$ N). Dashed lines in (f) through (l)
          represent pure strain flow $\alpha = \zeta$. Dashed lines in (m) through
          (o) represent geostrophic flow $\zeta = \frac{g}{f}\nabla_h^2 h$.}
 \label{fig3}
 \end{center}
\end{figure*}

>>>>

\title{Seasonality in governing dynamics at submesoscales}
%
% e.g., \title{Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$}
%

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.6\textwidth]{figs/fig3.pdf}
 \caption{Seasonal variation of joint probability distributions: vorticity vs.
          divergence (a through e), vorticity vs. strain rate (f through l).
          and vorticity vs. laplacian of sea-surface height (m through r).
          Dashed lines in (a) through (e) represent $\delta = \frac{\omega}{f_0}
          \zeta$ where $\omega = 2\pi/$(12 h, 3 h) and $f_0$ is the inertial frequency
          in the middle of the domain (32.5$^\circ$ N). Dashed lines in (f) through (l)
          represent pure strain flow $\alpha = \zeta$. Dashed lines in (m) through
          (o) represent geostrophic flow $\zeta = \frac{g}{f}\nabla_h^2 \eta$.}
 \label{fig3}
 \end{center}
\end{figure*}
